\documentclass{article}
\begin{document}
	\title{Project: RobBot}
	\author{Aditya, Anuj, Abhijit, Sayan\\IIIT Kalyani\\}
	\date{\today}
	\maketitle
%\tableofcontents
%\listoffigures
%\listoftables
	\begin{abstract}
	There are a lots of Chat-Bots out there and robots, but they are either too cheap or too costly for use. Our moto would be to make such small physical chat-bot that will communicate with us in natural languages like simple English (Hear \& Talk) and do some very basic movements using low cost Arduino at it's core. This would be our first step \& later we'll jump to extended features like machine learning and artificial intelligence.
	\end{abstract}
	\section{Phases:}
		\subsection{Requirement Engineering:}
		Types:
		\begin{enumerate}
			\item Functional Requirements(FR):
			\\What Functionalities \& Software Bahaviour Users Want
			\begin{enumerate}
				\item Good Calculation;
				\item Good data manipulation;
				\item Good Processing;
				\item Good logical decision-making.
			\end{enumerate}
			\item Non-Functional Requirements(NFR):
			\\System Requirements
			\begin{enumerate}
				\item Quality \& Attributes
				\item Design \& Architecture
			\end{enumerate}
			Cinsiderable things
			\begin{itemize}
				\item Performance
				\item Availability
				\item Maintability
				\item Portability
				\item Reliability
				\item Robustness
				\item Security
				\item Scability
				\item Tastability
				\item Usability
			\end{itemize}
			Approaches:
			\begin{itemize}
				\item Product Oriented:
				\item Process Oriented:
				\item Qualitative:
				\item Quantitative:
			\end{itemize}
			\item Interface Specification(IS):
			\\Link with Softwares
			\begin{itemize}
				\item Operating Systems: Linux, Windows, Mac, Android
				\item Databases: OracleSQL, MySQL, SQLite
				\item Database Connector: JDBC connector J
				\item Serial Communication: RxTx Library
				\item Program Uploader: Arduino IDE
			\end{itemize}
			Hardwares
			\begin{itemize}
				\item Computer HardDisk (to save Controlling Software)
				\item ArduinoUNO (atmel-328p)
				\item Breadboard, PCB, Wires \& connectors
				\item Motors \& Wheels
				\item Bluetooth/WiFi module
				\item Ultrasonic Sensors, Infrared Sensors
				\item Speakers
			\end{itemize}
		\end{enumerate}
		Steps:
		\begin{enumerate}
			\item Requirement Development:		
			\begin{itemize}
				\item Feasibility Study:
				\begin{itemize}
					\item Operational Feasibility:
\\Does the system serve the organizational objectives?	YES(requirements inside letter \& high usability in near future)
					\item Technical Feasibility:
\\Can the system be built using available technology in given time \& integrated with other surrounding systems as required by overall architecture?:	YES(Tech. Avail. OSs(Linux, Windows, Mac, Android), Arduino, Java, SQL)
					\item Economical Feasibility:
\\Can the system be built using available technology in given time and budget?	YES(OSs(Linux: Free (donation: optional), Windows: Rs. 8000(original) or free(pirated), Mac: Rs. 1000, Android: Rs. Rs. 10000...\emph{***If one has anyone of these, no need for extra cost execpt charging power}), ArduinoUNO(Rs. 500 approx.), Java, SQL: FREE; time=8 weeks...enough, budget=1000 Rs.)
				\end{itemize}
				\item Eliciting Requirements:
				\item Requirements Analysis:
				\item Specify and Validate Requirements:
			\end{itemize}
			\item Requirements Management:
		\end{enumerate}
		Models:
		\begin{enumerate}
			\item Structured Analysis Model:
			\item Object Oriented Analysis Model:
		\end{enumerate}
		\subsection{Designing:}
		\subsection{Coding \& Testing:}
		\subsection{Implementation:}
		\subsection{Maintenance:}
\end{document}
