\chapter{Overall Description}
\section{Product perspective}
In many companies there is a huge need of some little physical chat-bot at critical time, so this item would help them a lot.
\subsection{System Interfaces}
The RobBot system to be developed is a stand-alone tool consisting of 4 modules 
described below. The systems on which the program would run will be
	\begin{itemize}
		\item{Software} Computer(Linux) \& Android
		\item{Hardware} Arduino Genuino UNO
	\end{itemize}
	by default Java interface in each.
\subsection{User Interfaces}
The software has 4 modules,
	\begin{itemize}
		\item{User Authentication} Entry in the Software, by Registration \& Logging in;
		\item{Device Authentication} Device searching, selection \& connecting
		\item{Basic Operations} Basic movements with commands
		\item{Advance Operations} Artificial Intelligence using sensors, movements and commands \& responses
	\end{itemize}
	The databse interface is out of the normal users, but only for Admins \& developers.
\subsection{Software Interfaces}
The RobBot software would link-up with all devices required and start executing program.
\subsection{Communication Interfaces}
The communication sould be either serially or using WiFi network in the front-end \& with the database in the back-end.
\subsection{Memory constraints} quite big space (about 300MB for PC \& 100MB for android)
\subsection{Operations} The target operations would be Controlling the following,
	\begin{itemize}
		\item{Authorising} Security system
		\item{Manage}	Users
		\item{Robot's Actions}
		\begin{itemize}
			\item{Movement} Basic movements
			\item{Sense} Analyzing sensors' data
			\item{Interprete} Text to Speech and \textit{vice versa}
			\item{Thiking} Learning \& intelligence
		\end{itemize}
	\end{itemize}
	of the Robot.
\subsection{Site adaptation requirements}
No specific site adaptation is required.
\section{Product functions}
The two main function for this Software would be Authentication \& manage users, and the other one would be to control over the Bot device \& all the main features discussed before.
\section{User characteristics}
Users should be much familier with what they are doing. If they command the bot to do something that tries to break the rules of the Robots, the bot will not work accordingly.
\section{Constraints}
The device might be hacked and damaged by applying physical pressure on it.
\section{Assumptions \& dependencies}
Not specified.
\section{Apportioning of requirements}
The connection issue between the software \& the hardware.
